DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-06 paper/comparison.tex
comparision revision (WIP)

In this section, we compare three computing platforms---the Raspberry
Pi 3, the Intel UP~\footnote{http://www.up-board.org/up/} and NVIDIA
Jetson
TX2~\footnote{http://www.nvidia.com/object/embedded-systems-dev-kits-modules.html}---from
the point of view of supporting vision-based end-to-end deep learning
based autonomous vehicles.

Table~\ref{tbl:platforms}

Our basic approach is to use the same DeepPicar's software, and repeat
the experiments in Section~\ref{sec:evaluation} on each hardware
platform and compare the results.

@@

The results of the multicore tests can be seen in 
Figure~\ref{fig:sys_core}. It was found that the both the Tegra TX2 
and the Intel UP Board performed better than the Raspberry Pi 3 in 
all experiments. On average, the UP was able to perform inferencing 
operations, at least, twice as fast as the Raspberry Pi 3. The 
difference was even greater with the TX2, as control loops, in the 
worst case, were 3x faster using only the CPU and 10x quicker when 
using the GPU. As a result, they were all able to satisfy the 50 ms 
WCET by a very clear margin (in the worst case, the UP Board would 
still meet it by $\sim$20 ms), and, thus, demonstrates that they are 
more capable of autonomous driving than the Raspberry Pi 3.

>>>>

In this section, we compare three computing platforms---the Raspberry
Pi 3, the Intel UP~\footnote{http://www.up-board.org/up/} and NVIDIA
Jetson
TX2~\footnote{http://www.nvidia.com/object/embedded-systems-dev-kits-modules.html}---from
the point of view of supporting vision-based end-to-end deep learning
based autonomous vehicles. 
Table~\ref{tbl:platforms} shows architectural features of the three
platforms~\footnote{Note that the GPUs of the Raspberry Pi 3 and Intel
  Up are not used in evaluation due to lack of software (TensorFlow)
support. Also, the two Denvor cores in Tegra TX2 are not used in
evaluation due to TensorFlow issues.}.

Our basic approach is to use the same DeepPicar software, and repeat
the experiments in Section~\ref{sec:evaluation} on each hardware
platform and compare the results. 
For Tegra TX2, we have two different system configurations,
which differ in whether TensorFlow is configured to use its GPU or
only the CPU cores. Thus, the total four system configurations are
compared.

@@

Figure~\ref{fig:sys_core} shows the average control loop completion
timing as a function of the number of CPU cores on each of the four
system configurations.
It was found that the both the Tegra TX2 
and the Intel UP Board performed better than the Raspberry Pi 3 in 
all experiments. On average, the UP was able to perform inferencing 
operations, at least, twice as fast as the Raspberry Pi 3. The 
difference was even greater with the TX2, as control loops, in the 
worst case, were 3x faster using only the CPU and 10x quicker when 
using the GPU. As a result, they were all able to satisfy the 50 ms 
WCET by a very clear margin (in the worst case, the UP Board would 
still meet it by $\sim$20 ms), and, thus, demonstrates that they are 
more capable of autonomous driving than the Raspberry Pi 3.

### 2017-10-06 paper/evaluation.tex
Update control loop graph
Also changed location of training loss graph
comparision revision (WIP)

The Raspberry Pi 3 Model B platform used in DeepPicar equip a Boardcom
BCM2837 SoC, which has a quad-core 64bit ARM Cortex-A53 cluster,
running at up to 1.2GHz. Each core has 16K private I\&D caches, and all
cores share a 512KB L2 cache.
The chip also includes Broadcom's Videocore IV
GPU, although we did not use the GPU in our evaluation due to the lack
of sofware support (Tensorflow is not compatible with the GPU).
For software, we use Ubuntu MATE 16.04, Tensorflow 1.1 and python
2.7. We disabled DVFS (dynamic voltage frequency scaling) and
configure the clock speed of each core at the maximum 1.2GHz.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=.45\textwidth]{Total_Processing_Time}
  \caption{DeepPicar's control loop processing times over 1000 input image frames.}
  \label{fig:control-loop-timing}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/perf_vs_corecnt}
  \caption{Average control loop execution time vs. \#of CPU
    cores. \fixme{instead of the total control loop time, use the
      average of DNN inferencing time.}}
  \label{fig:perf-vs-corecnt}
\end{figure}

@@

\begin{table*}[h]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    Item    & Raspberry Pi 3 (B)   & Intel UP                  & NVIDIA Jetson TX2\\
    \hline
            & BCM2837              & X5-Z8350 (Cherry Trail)   & Tegra TX2 \\
    CPU     & 4x Cortex-A53@1.2GHz/512KB L2  &
              4x Atom@1.92GHz/2MB L2 &
              4x Cortex-A57@2GHz/2MB L2 \\
            &              &              & 2x Denver@2.0GHz/2MB L2 (not used)  \\
    \hline
    GPU     &  VideoCore IV (not used)    &
               Intel HD 400 Graphics (not used) &
               Pascal 256 CUDA cores   \\
    \hline
    Memory  & 1GB LPDDR2   &  2GB DDR3L     & 8GB LPDDR4              \\
    \hline
  \end{tabular}
  \caption{Compared embedded computing platforms}
  \label{tbl:patforms}
\end{table*}

>>>>

The Raspberry Pi 3 Model B platform used in DeepPicar equips a Boardcom
BCM2837 SoC, which has a quad-core 64bit ARM Cortex-A53 cluster,
running at up to 1.2GHz. Each core has 16K private I\&D caches, and all
cores share a 512KB L2 cache.
The chip also includes Broadcom's Videocore IV
GPU, although we did not use the GPU in our evaluation due to the lack
of sofware support (Tensorflow is not compatible with the GPU).
For software, we use Ubuntu MATE 16.04, Tensorflow 1.1 and python
2.7. We disabled DVFS (dynamic voltage frequency scaling) and
configure the clock speed of each core at the maximum 1.2GHz.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=.5\textwidth]{figs/Fig7_new}
  \caption{DeepPicar's control loop processing times over 1000 input image frames.}
  \label{fig:control-loop-timing}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/perf_vs_corecnt}
  \caption{Average control loop execution time vs. \#of CPU
    cores.}
  \label{fig:perf-vs-corecnt}
\end{figure}
    %% \fixme{instead of the total control loop time, use the
    %%   average of DNN inferencing time.}}

@@

\begin{table*}[h]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    Item    & Raspberry Pi 3 (B)   & Intel UP                  & NVIDIA Jetson TX2\\
    \hline
            & BCM2837              & X5-Z8350 (Cherry Trail)   & Tegra TX2 \\
    CPU     & 4x Cortex-A53@1.2GHz/512KB L2  &
              4x Atom@1.92GHz/2MB L2 &
              4x Cortex-A57@2GHz/2MB L2 \\
            &              &              & 2x Denver@2.0GHz/2MB L2 (not used)  \\
    \hline
    GPU     &  VideoCore IV (not used)    &
               Intel HD 400 Graphics (not used) &
               Pascal 256 CUDA cores   \\
    \hline
    Memory  & 1GB LPDDR2   &  2GB DDR3L     & 8GB LPDDR4              \\
    \hline
  \end{tabular}
  \caption{Compared embedded computing platforms}
  \label{tbl:platforms}
\end{table*}
